Solar-Electric and Gas Powered, Long-Endurance UAV Sizing via Geometric Programming

### 2017-04-19 docs/paperin_review.tex
change ft to m for lapse rate and climb rate

The lapse is calculated from the required flight altitude $h=15,000$ [ft], prior to the optimization solve using an approximate engine loss rate for normally aspirated engines of 3.5\% hp per 1000 ft,\cite{enginelapse}

\begin{equation}
    \label{e:lapsefit}
    L_{\text{eng}}(h) = 1 - \frac{0.035}{1000 \text{ [ft]}} h.
\end{equation}

@@

\begin{equation}
    \label{e:climbrate}
    \dot{h} \geq 100 \text{ [ft/min]}.
\end{equation}

>>>>

The lapse is calculated from the required flight altitude $h=4,500$ [m], prior to the optimization solve using an approximate engine loss rate for normally aspirated engines of 3.5\% hp per 300 m,\cite{enginelapse}

\begin{equation}
    \label{e:lapsefit}
    L_{\text{eng}}(h) = 1 - \frac{0.035}{300 \text{ [m]}} h.
\end{equation}

@@

\begin{equation}
    \label{e:climbrate}
    \dot{h} \geq 30 \text{ [m/min]}.
\end{equation}
